Drought frequency predicts life history strategies in \emph{Heliophila}

### 2018-12-01 manuscript/manuscript.Rmd
species #

### Life history data for_ Heliophila_
_Heliophila_ is a genus of flowering plants endemic to the southern portion of Africa including the Cape Floristic and Succulent Karoo Regions. These are among the most botanically diverse environments on Earth and the estimated ~50 _Heliophila_ species occurring there are considered to make up the most diverse genus of the family Brassicaceae [@mummenhoff2005phylogeny;@mandakova2012whole]. This genus includes both perennial and annual species and this change in life history strategy has likely arisen multiple independent times [@appel1997generic;@mummenhoff2005phylogeny]. Furthermore, the fine scale climatic heterogeneity of Southern Africa is ideal for studying the distribution of traits in relation to environmental parameters [@sayre2013new]. We used life histories reported by @mummenhoff2005phylogeny, grouping species with annual or perennial life histories. Perenniality was defined based any form of perennial life history (e.g., herbs, shrubs, mixed, etc). Because the nature of species reported with mixed traits were unknown (i.e. plasticity vs. genetic variation), we classified these species here as perennial since they can maintain vegetative growth after reproduction at least to some capacity.

>>>>

### Life history data for_ Heliophila_
_Heliophila_ is a genus of flowering plants endemic to the southern portion of Africa including the Cape Floristic and Succulent Karoo Regions. These are among the most botanically diverse environments on Earth and the _Heliophila_ species occurring there are considered to make up the most diverse genus of the family Brassicaceae [@mummenhoff2005phylogeny;@mandakova2012whole]. This genus includes both perennial and annual species and this change in life history strategy has likely arisen multiple independent times [@appel1997generic;@mummenhoff2005phylogeny]. Furthermore, the fine scale climatic heterogeneity of Southern Africa is ideal for studying the distribution of traits in relation to environmental parameters [@sayre2013new]. We used life histories reported by @mummenhoff2005phylogeny, grouping species with annual or perennial life histories. Perenniality was defined based any form of perennial life history (e.g., herbs, shrubs, mixed, etc). Because the nature of species reported with mixed traits were unknown (i.e. plasticity vs. genetic variation), we classified these species here as perennial since they can maintain vegetative growth after reproduction at least to some capacity.

### 2018-12-01 manuscript/manuscript.tex
species #

\emph{Heliophila} is a genus of flowering plants endemic to the southern
portion of Africa including the Cape Floristic and Succulent Karoo
Regions. These are among the most botanically diverse environments on
Earth and the estimated \textasciitilde{}50 \emph{Heliophila} species
occurring there are considered to make up the most diverse genus of the
family Brassicaceae (Mandáková et al., 2012; Mummenhoff et al., 2005).
This genus includes both perennial and annual species and this change in
life history strategy has likely arisen multiple independent times
(Appel and Al-Shehbaz, 1997; Mummenhoff et al., 2005). Furthermore, the
fine scale climatic heterogeneity of Southern Africa is ideal for
studying the distribution of traits in relation to environmental
parameters (Sayre et al., 2013). We used life histories reported by
Mummenhoff et al. (2005), grouping species with annual or perennial life
histories. Perenniality was defined based any form of perennial life
history (e.g., herbs, shrubs, mixed, etc). Because the nature of species
reported with mixed traits were unknown (i.e.~plasticity vs.~genetic
variation), we classified these species here as perennial since they can
maintain vegetative growth after reproduction at least to some capacity.

>>>>

\emph{Heliophila} is a genus of flowering plants endemic to the southern
portion of Africa including the Cape Floristic and Succulent Karoo
Regions. These are among the most botanically diverse environments on
Earth and the \emph{Heliophila} species occurring there are considered
to make up the most diverse genus of the family Brassicaceae (Mandáková
et al., 2012; Mummenhoff et al., 2005). This genus includes both
perennial and annual species and this change in life history strategy
has likely arisen multiple independent times (Appel and Al-Shehbaz,
1997; Mummenhoff et al., 2005). Furthermore, the fine scale climatic
heterogeneity of Southern Africa is ideal for studying the distribution
of traits in relation to environmental parameters (Sayre et al., 2013).
We used life histories reported by Mummenhoff et al. (2005), grouping
species with annual or perennial life histories. Perenniality was
defined based any form of perennial life history (e.g., herbs, shrubs,
mixed, etc). Because the nature of species reported with mixed traits
were unknown (i.e.~plasticity vs.~genetic variation), we classified
these species here as perennial since they can maintain vegetative
growth after reproduction at least to some capacity.
